---
title: "simpleRegress"
author: "Desiree De La Rosa"
date: "summer 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE)
```
## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).

I am going to try to a model of the length of the the bear based off of the size of the chest.

```{r}
mychest <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(mychest)
summary.lm(mychest)
```

The mychest model is using chest instead of neck as used in the simp model, using chest adjusted the r squared and is 0.786 and the residual standard error is 4.939. In the simp model the r squared was 0.747 and the residual standard error was 5.376.The my chest is a better model because it explains the error and the residual error is smaller than in the simp model.


